Theories of deliberated choice

### 2023-06-21 simple.tex
Further notations

Given $\hist \in \allhist$ and $\ar_k, \ar_l \in \allargs$, let $(\hist, \ar_k, ?, ✗, …, \ar_l, ?)$ denote the set $\set{\histl \suchthat \exists \histk \suchthat \hist \subset \histk \subset \histl \suchthat \ar_k \in \histkend \land \histk \nileadsto \phi \land \ar_l \in \histlend}$.

\begin{theorem}
	Given any $\phi \in P, \ar_k, \ar_l \in \allargs$, consider the following claim $C$: 
	\begin{equation}
		\left\{\begin{aligned}
			&\forall i \in I, \hist \in \allhist \suchthat \ar_k \in \histend \land \hist \nileadstog \phi: \set{\histp \suchthat \hist \subseteq \histp \land \ar_l \in \histpend} \ileadstog \phi;\\
			&\forall i \in I, \hist \in \allhist \suchthat \ar_l \in \histend \land \hist \nileadstog \phi: \set{\histp \suchthat \hist \subseteq \histp \land \ar_k \in \histpend} \ileadstog \phi.
		\end{aligned}\right.
	\end{equation}
	In short,
	$\forall \hist: [\ar_k \in \histend \land \hist \nileadstog \phi] \implies (\hist, …, \ar_l, ?) \ileadstog \phi$.
	In shorter,
	$(\hist, \ar_k, ?, \text{\ding{55}}, …, \ar_l, ?) \ileadstog \phi$, which is $\set{\histl \suchthat \exists \histk \suchthat \hist \subset \histk \subset \histl \suchthat \ar_k \in \histkend \land \ar_l \in \histlend \land \histk \nileadsto \phi}$.

>>>>

Given $\hist \in \allhist$ and $\ar_k, \ar_l \in \allargs$, let $(\hist, \ar_k, ?, ✗, …, \ar_l, ?)$ denote the set 
$\set{\histl \suchthat \exists \histk \suchthat \hist \subset \histk \subset \histl \land \ar_k \in \histkend \land \histk \nileadsto \phi \land \ar_l \in \histlend}$.
Given $\ar_k, \ar_l \in \allargs$, let $(…, \ar_k, ?, ✗, …, \ar_l, ?)$ denote the set 
$\cup_{\hist \in \allhist} (\hist, \ar_k, ?, ✗, …, \ar_l, ?) = 
\set{\histl \suchthat \exists \hist, \histk \suchthat \hist \subset \histk \subset \histl \land \ar_k \in \histkend \land \histk \nileadsto \phi \land \ar_l \in \histlend} = 
\set{\histl \suchthat \exists \histk \suchthat \histk \subset \histl \land \ar_k \in \histkend \land \histk \nileadsto \phi \land \ar_l \in \histlend}$.

\begin{theorem}
	Given any $\phi \in P, \ar_k, \ar_l \in \allargs$, consider the following claim $C$: $\forall i \in I$,
	\begin{equation}
		\left\{\begin{aligned}
			&\forall \histk \in \allhist \suchthat \ar_k \in \histkend \land \histk \nileadstog \phi: \set{\histl \suchthat \histk \subseteq \histl \land \ar_l \in \histlend} \ileadstog \phi;\\
			&\forall \hist \in \allhist \suchthat \ar_l \in \histend \land \hist \nileadstog \phi: \set{\histp \suchthat \hist \subseteq \histp \land \ar_k \in \histpend} \ileadstog \phi.
		\end{aligned}\right.
	\end{equation}
	In short,
	$\forall \hist: [\ar_k \in \histend \land \hist \nileadstog \phi] \implies (\hist, …, \ar_l, ?) \ileadstog \phi$.
	In shorter,
	$(\hist, \ar_k, ?, \text{\ding{55}}, …, \ar_l, ?) \ileadstog \phi$, which is $\set{\histl \suchthat \exists \histk \suchthat \hist \subset \histk \subset \histl \suchthat \ar_k \in \histkend \land \ar_l \in \histlend \land \histk \nileadsto \phi}$.
